Are iPhone users more secure when using mobile enterprise systems?

### 2021-04-20 outputs/paper/paper.Rmd
update

## Examining covariate balance in the matched sample

@@

## T-test

The t-test is used to compare the sample mean of our Treated group and Control group. The goal is to determine whether the intervention has an effective effect on the treated group. Our hypothesis is the intervention will have positive impact towards the restaurant's revenue . The t-test results is represented in the table xxx. The package **Broom** [@broom1] is used to clean the t test results and convert it into the dataframe. The p value we get is < 2.2e-16, as the p value would indicate a significant result, meaning that the actual p value is even smaller than 2.2e-16 (a typical threshold is 0.05, anything smaller counts as statistically significant). So we can 
interpret hypothesis not rejected which means that the re-opening of restaurants has a significant effect on treated group in terms of revenue increase.

## correlation model

## regression model 
We are using RStudio to run the multiple linear regression model. The following reasons explain why we decide to choose multiple linear regression [@WinNT]:

@@

>>>>

## Model check---Examining covariate balance in the matched sample

@@

## Estimating treatment effects---T-test

The t-test is used to compare the sample mean of our Treated group(IOS) and Control group(Android). The goal is to determine whether the intervention has an effective effect on the treated group. Our hypothesis is that the intervention will increase the perceived ES security. The t-test results will be presented in the next section. The package **Broom** [@broom1] is used to clean the t test results and convert it into the dataframe.

```{r ttest, fig.cap = "T-test",echo=FALSE, warning=FALSE,fig.width=8, fig.height=4}
## T test
ttest_after<-with(dta_m, t.test(PSave ~ treat))
ttest_after
tidy(ttest_after)%>%
  select(-c(estimate,statistic,parameter))%>%

  kableExtra::kbl(caption = "T-test on dependent variable") %>%  
  kableExtra::kable_styling(latex_options = "scale_down")%>% # use scale_down option to make the font
  kableExtra::kable_styling(latex_options = c("hold_position"))
```

## Estimating treatment effects---regression model 
We are using RStudio to run the multiple linear regression model. The following reasons explain why we decide to choose multiple linear regression [@WinNT]:

@@

The p value we get is < 2.2e-16, as the p value would indicate a significant result, meaning that the actual p value is even smaller than 2.2e-16 (a typical threshold is 0.05, anything smaller counts as statistically significant). So we can interpret hypothesis not rejected which means that the re-opening of restaurants has a significant effect on treated group in terms of revenue increase.
